Developing an automated iterative near-term forecasting system for an ecological

### 2018-08-27 manuscript/portal_iterative_forecasting_ms.Rmd
Update pdf and html versions

---
title: Developing an automated iterative near-term forecasting system for an ecological
  study
author: Ethan P. White$^{1,2,3}$, Glenda M. Yenni$^1$, Shawn D. Taylor$^4$, Erica
  M. Christensen$^1$, Ellen K. Bledsoe$^4$, Juniper L. Simonis$^1$, S. K. Morgan Ernest$^{1,3}$
csl: mee.csl
output:
  html_document: default
  pdf_document:
    keep_tex: yes
geometry: left=3.5cm, right=3.5cm, top=2.25cm, bottom=2.25cm, headheight=12pt, letterpaper
header-includes:
- \usepackage{times}
- \usepackage{setspace}
- \usepackage{booktabs}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
fontsize: 12pt
bibliography: refs.bib
---
\raggedright

>>>>

---
title: Developing an automated iterative near-term forecasting system for an ecological
  study
author: Ethan P. White$^{1,2,3}$, Glenda M. Yenni$^1$, Shawn D. Taylor$^4$, Erica
  M. Christensen$^1$, Ellen K. Bledsoe$^4$, Juniper L. Simonis$^1$, S. K. Morgan Ernest$^{1,3}$
csl: mee.csl
output:
  pdf_document:
    keep_tex: yes
  html_document: default
geometry: left=3.5cm, right=3.5cm, top=2.25cm, bottom=2.25cm, headheight=12pt, letterpaper
header-includes:
- \usepackage{times}
- \usepackage{setspace}
- \usepackage{booktabs}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
fontsize: 12pt
bibliography: refs.bib
---
\raggedright
